---
title: "dMACS_Shrunk Example"
author: "Conor Lacey"
date: '2023-02-26'
output: github_document
---

```{r packages}
rm(list = ls())
suppressWarnings(library(tidyverse))
suppressWarnings(library(faux))
```


### Introduction 

So this is meant to demonstrate how dMACS_Shrunk should theoretically work with some fake data I created. In this demonstration I use just one item for simplicity sake.

### Fake Data

```{r fake-data}
set.seed(1489)

fakedatR <- rnorm_multi(n = 500, 
                          mu = c(5, 4), 
                          sd = c(1, 1), 
                          r = c(0.1), 
                          varnames = c("Eta", "Response"))

fakedatR$Response <- fakedatR$Response %>% round()
fakedatR$Response <- if_else(fakedatR$Response > 10, 10, fakedatR$Response)

fakedatR <- fakedatR %>% mutate (group = "R")

fakedatF <- rnorm_multi(n = 500, 
                          mu = c(5,8), 
                          sd = c(1, 1), 
                          r = c(0.9), 
                          varnames = c("Eta", "Response"))

fakedatF$Response <- fakedatF$Response %>% round()
fakedatF$Response <- if_else(fakedatF$Response > 10, 10, fakedatF$Response)

fakedatF <- fakedatF %>% mutate (group = "F")

fakedat <- bind_rows(fakedatR, fakedatF)

fakedat %>% ggplot(aes(x = Eta, y = Response, color = group)) + 
  geom_point(alpha = 0.4) + 
  stat_smooth(method = lm, se = FALSE, linewidth = 1.5) + 
  labs(x = "Latent Trait",
       color = "Group") + 
  scale_color_discrete(labels = c("Focal", "Reference"))
```

Awesome. Fake data created. To clarify I have to add the participants estimated latent score for the reference group given that the formula requires this in the calculation. The estimated latent score must of course also correlate with the item hence why I use the rnorm_multi() function from the "faux" package. However, the bigger picture that should be seen here is that there is clearly an interaction effect based on what group you belong to. The group assignment is clearly affecting the item's loading and intercept. 

### Calculating dMACS

```{r dMACS}
eta<-seq(0,8, by = 0.5)
linearR <- lm(fakedatR$Response ~ fakedatR$Eta)
linearF <- lm(fakedatF$Response ~ fakedatF$Eta)

aR <- linearR$coefficients[1]
bR <- linearR$coefficients[2]

aF <- linearF$coefficients[1]
bF <- linearF$coefficients[2]

a <- (nrow(fakedatR)-1)*sd(fakedatR$Response)+(nrow(fakedatF)-1)*sd(fakedatF$Response)
b <- (nrow(fakedatR)-1) + (nrow(fakedatF)-1) 

den <- a/b

integrand <- function(x){
  ((aF + bF*x)-(aR + bR*x))*dnorm(x,5,1)
}

dMACS<-sqrt(integrate(integrand, -Inf, Inf)$value)/den

dMACS
```

Phew! That's pretty dang big. I suspect it's not typical to find a value this large, however for the purposes of this example we can definitley say that this item in non-invariant. However, now let's see how much is shrunk using the spike-and-slab method

### Spike-and-Slab
```{r}


```

